A comparative analysis of AquaMaps and IUCN species distribution maps

### 2015-12-12 R/data_explore_global_maps.Rmd
created all-IUCN level plot

am_spp_cells_big <- fread(file.path(dir_am_data, 'hcaf_sp_native_trunc.csv')) %>%
  as.data.frame()
# ### am_spp_cell_big is missing loiczid info so bring in hcaf to match
# 
# hcaf <- fread(file.path(dir_anx, 'raw/aquamaps_2014/tables/hcaf.csv')) %>% #bring this in just to get loiczid
#   as.data.frame() %>%
#   dplyr::select(CsquareCode, LOICZID) %>%
#   rename(loiczid = LOICZID)

### find total spp to allow for percent calcs later
am_all_n_tot <- am_spp_cells_big %>% 
  dplyr::select(SpeciesID) %>% 
  unique() %>% nrow()

all_am <- am_spp_cells_big %>%
  dplyr::select(SpeciesID, CsquareCode) %>%
  group_by(CsquareCode) %>%
  summarize(all_count = n(),
            all_pct   = all_count/am_all_n_tot) %>%
  as.data.frame()

all <- all_am %>%
  left_join(hcaf, by = 'CsquareCode')

all_am_map <- subs(loiczid_raster, all[ , c('loiczid', 'all_count')], 
                   by = 'loiczid', 
                   which = 'all_count', 
                   subsWithNA = TRUE)

@@

>>>>

am_spp_cells_big <- fread(file.path(dir_am_data, 'hcaf_sp_native_trunc.csv')) %>%
  as.data.frame(stringsAsFactors = FALSE)

### find total spp to allow for percent calcs later
# am_all_n_tot <- am_spp_cells_big %>% 
#   dplyr::select(SpeciesID) %>% 
#   unique() %>% nrow()

all_am <- am_spp_cells_big %>%
  group_by(loiczid) %>%
  summarize(all_count = n()) %>%
#   summarize(all_count = n(),
#             all_pct   = all_count/am_all_n_tot) %>%
  as.data.frame()

all_am_map <- subs(loiczid_raster, all_am[ , c('loiczid', 'all_count')], 
                   by = 'loiczid', 
                   which = 'all_count', 
                   subsWithNA = TRUE)

@@

Now look at full IUCN species

iucn_cells_file    <- file.path(dir_data_iucn, 'iucn_cells_2015.csv')
iucn_spp_cells_all <- fread(iucn_cells_file) %>%
      as.data.frame(stringsAsFactors = FALSE)

### find total spp to allow for percent calcs later
# am_all_n_tot <- am_spp_cells_big %>% 
#   dplyr::select(SpeciesID) %>% 
#   unique() %>% nrow()

all_iucn <- iucn_spp_cells_all %>%
  group_by(loiczid) %>%
  summarize(all_count = n()) %>%
#   summarize(all_count = n(),
#             all_pct   = all_count/am_all_n_tot) %>%
  as.data.frame()

all_iucn_map <- subs(loiczid_raster, all_iucn[ , c('loiczid', 'all_count')], 
                   by = 'loiczid', 
                   which = 'all_count', 
                   subsWithNA = TRUE)

levelplot(all_iucn_map, par.settings = myTheme, main = 'Entire IUCN Dataset')
```
